Halo alignments with large scale tidal and velocity fields

### 2013-02-26 paper/main.tex
added basic theoretical references to compare with
historical data

\end{abstract}
\begin{keywords}
galaxies: high-redshift - galaxies: star formation - line: formation
\end{keywords}

@@

\citep[e.g.][]{Pritchard10}.  
%-------

@@

\section{N-body simulation and halo finding}

>>>>

\end{abstract}
\begin{keywords}
methods: N-body simulations, galaxies: haloes, cosmology: theory, dark matter, large-scale structure of Universe
\end{keywords}

@@

%-------

@@

\citep{Libeskind2013} %various alignments
\citep{Codis2012}
\citep{Faltenbacher2009} %galaxy alignments with mocks
\citep{Paz2008} %angular momentum alignments
\citep{Platen2008} %alignment in voids
\citep{AragonCalvo2007} %Spin alignment
\citep{Lee2007}%Obs. spin alignment
\citep{Hahn2007}% various alignments with the Tweb

\begin{itemize}
\item 
\citep{Lee2002}%Obs. spin alignment
Observational measurement for the alignment of galaxy spin axes with
the local tidal shear field. For the measurement of shear, we have used
the Point Source Catalog Redshift (PSCz) survey (a complete redshift survey
from the IRAS Point Source Catalog) data. This was done down to a
radial comoving distance of $\sim 150$\hMpc.
\item
\citep{Hatton2001} %angular momentum alignment
DM matter only simulation. $256^3$ particles, $100$\hMpc, particle
mass. Look for mutual alignment of angular momentum vectors, and
alignment with structure. halos on any escale by close pair
statistics. They don't find any evidence for a statistically significant mutual
alignment of haloes on any scale,
\end{itemize}
\section{N-body simulation and halo finding}
